EuringPosterFigures

### 2021-04-27 scripts/EuringPosterFigures.Rmd
bias across life history scenarios

```{r not using but keep for now}

### Keep to look at difference in bias across scenarios
# #get posterior medians
# low.meds <- low.dat %>%
#   dplyr::select('phi1.obs', 'phi1.true', 'phiad.obs', 'phiad.true', 'fec.obs', 'fec.true',
#                             'sims', 'scenario', 'simscenarios') %>%
#   reshape2::melt(id.vars = c('sims', 'scenario', 'simscenarios')) %>%
#   group_by(scenario, simscenarios, variable) %>%
#   summarize(median = median(value)) %>%
#   reshape2::dcast(scenario + simscenarios ~ variable, value.var = 'median') %>%
#   #calculate relative bias
#   transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true, 
#             phiad.bias = (phiad.obs-phiad.true)/phiad.true, 
#             fec.bias = (fec.obs-fec.true)/fec.true)
# 
# #just bias
# low.bias <- low.meds %>%
#   dplyr::select('scenario', 'simscenarios', 'phi1.bias', 'phiad.bias', 'fec.bias') %>%
#   reshape2::melt(id.vars = c('scenario', 'simscenarios')) %>%
#   transform(simscenarios = factor(simscenarios, labels = c('lam = low; p=L', 'M', 'H')))
# 
# ggplot(low.bias, aes(x = factor(scenario), y = variable, fill = value)) +
#   geom_tile() +
#   xlab('Scenario') + ylab('Parameter') +
#   facet_grid(~simscenarios, drop = T, scales = 'free_x') +
#   scale_fill_gradient2(name = "Relative bias",
#                       mid = "#FFFFFF", low = "#012345", high = "#012345", midpoint = 0) +
#   theme_bw() +
#   theme(legend.position = 'top',
#              strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

>>>>

```{r bias across life history scenarios}

##Same as above but looking at the variability across data-generating true values for phiad, phi1, fec

#get posterior medians; same as above except keep 'scenario' in group_by
all.meds <- all.dat %>%
  dplyr::select('phi1.obs', 'phi1.true', 'phiad.obs', 'phiad.true', 'fec.obs', 'fec.true',
                            'sims', 'scenario', 'simscenarios', 'lambda.scenario') %>%
  reshape2::melt(id.vars = c('sims', 'scenario', 'simscenarios', 'lambda.scenario')) %>%
  group_by(lambda.scenario, scenario, simscenarios, variable) %>%
  summarize(median = median(value)) %>%
  reshape2::dcast(lambda.scenario + scenario + simscenarios ~ variable, value.var = 'median') %>%
  #calculate relative bias
  transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true,
            phiad.bias = (phiad.obs-phiad.true)/phiad.true,
            fec.bias = (fec.obs-fec.true)/fec.true)

#just bias; same as above, keep 'scenario'
rel.bias <- all.meds %>%
  dplyr::select('lambda.scenario', 'scenario', 'simscenarios', 
                'phi1.bias', 'phiad.bias', 'fec.bias') %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'simscenarios')) %>%
  transform(simscenarios = factor(simscenarios, labels = rep(c('L', 'M', 'H'),3)))

#grab true values from above
true_vals <- all.dat %>%
  distinct(lambda.scenario, scenario, phiad.true, fec.true, phi1.true) %>%
  transform(phiad.true = round(phiad.true,1),
            phi1.true = round(phi1.true,1), fec.true = round(fec.true,1))

#merge back onto bias df so can have something to name/view the 'scenarios' 
rel.bias.vals <- rel.bias %>%
  merge(true_vals, by = c('lambda.scenario', 'scenario'))

#scenario number -- not a useful view, but inspired this investigation
ggplot(rel.bias, aes(x = factor(scenario), y = variable, fill = value)) +
  geom_tile() +
  xlab('Scenario') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "Relative bias",
                      mid = "#FFFFFF", low = "#012345", high = "#012345", midpoint = 0) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

#view by fec.true
ggplot(rel.bias.vals, aes(x = factor(fec.true), y = variable, fill = value)) +
  geom_tile() +
  xlab('True fecundity') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "Relative bias",
                      mid = "#FFFFFF", low = "#012345", high = "#012345", midpoint = 0) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

#view by phiad.true
ggplot(rel.bias.vals, aes(x = factor(phiad.true), y = variable, fill = value)) +
  geom_tile() +
  xlab('True phi.ad') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "Relative bias",
                      mid = "#FFFFFF", low = "#012345", high = "#012345", midpoint = 0) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

#view by phi1.true
ggplot(rel.bias.vals, aes(x = factor(phi1.true), y = variable, fill = value)) +
  geom_tile() +
  xlab('True phi.1') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "Relative bias",
                      mid = "#FFFFFF", low = "#012345", high = "#012345", midpoint = 0) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))
